\bf On semidefinite-representable sets over valuation fields

### 2025-05-15 article/paper_padic_spec.tex
notation null and identity matrix

The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
with coefficients in $K$ is denoted by $K[x]_{d}$. The ring of matrices of
size $p \times q$ with entries in a ring $R$ is $R^{p \times q}$ and the general
linear group in $R^{n \times n}$ is $\GL_n(R)$.
For the sake
of ease of writing, block-diagonal matrices with blocks $B_1,\ldots,B_d$ are denoted by
$\diag(B_1, \ldots, B_d)$.

We recall the definition of Smith Normal Form, in our context.
\begin{definition}[Smith Normal Form]\label{smith_nf}
  Let $M \in K^{m \times n}$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
  $$
  SNF(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r})
  $$
  where ${\bf 0}_{t}$ is a null square matrix of size $t$.
  The matrix $SNF(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
  \emph{invariant factors}.
\end{definition}
\begin{remark}
  The valuation of the first invariant factor of $SNF(M)$ of a matrix
  $M \in K^{n \times n}$ is the minimum of the valuations of the entries of
  $M$. In particular, $SNF(M) \in \OK^{n \times n}$.
\end{remark}

@@

A \emph{linear programming problem} (or simply \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
as:
\begin{equation}
  \tag{LP}\label{LP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in K^n} & \val(\left\langle c, x \right\rangle) \\
  &    & \text{s.t.}         & A x + b \geq 0\\
  & & & D x = e
\end{array}
\end{equation}
with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in \allmat_{d,n}(K)$, $b \in K^d$, $D \in \allmat_{m,n}$, $e \in K^m$ 
and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$. When $A$ is a diagonal matrix and $D = 0$, we often
refer to \eqref{LP} as a \emph{diagonal} linear program. We denote the \emph{feasible set} of \eqref{LP} by
\begin{equation*}
\begin{aligned}
  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
\end{aligned}
\end{equation*}
A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$
is called a \emph{solution} to \eqref{LP} if $p^* = \left\langle c,x^*\right\rangle$.

>>>>

The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
with coefficients in $K$ is denoted by $K[x]_{d}$. The ring of matrices of
size $p \times q$ with entries in a ring $R$ is $R^{p \times q}$ and the general
linear group in $R^{n \times n}$ is $\GL_n(R)$.
For the sake of ease of writing, block-diagonal matrices with blocks
$B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null square
matrix of size $t$ by ${\bf 0}_{t}$, and the identity matrix by $I_t$.

We recall the definition of Smith Normal Form, in our context.
\begin{definition}[Smith Normal Form]\label{smith_nf}
  Let $M \in K^{m \times n}$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
  $$
  SNF(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r}).
  $$
  The matrix $SNF(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
  \emph{invariant factors}.
\end{definition}
\begin{remark}
  The valuation of the first invariant factor of $SNF(M)$ of a matrix
  $M \in K^{n \times n}$ is the minimum of the valuations of the entries of
  $M$. In particular, $SNF(M) \in \OK^{n \times n}$.
\end{remark}

@@

A \emph{linear programming problem} (or \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
as:
\begin{equation}
  \tag{LP}\label{LP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in K^n} & \val(\left\langle c, x \right\rangle) \\
  &    & \text{s.t.}         & A x + b \geq 0\\
  & & & D x = e
\end{array}
\end{equation}
with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in \allmat_{d,n}(K)$, $b \in K^d$, $D \in \allmat_{m,n}$, $e \in K^m$ 
and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$. When $A$ is a diagonal matrix and $D = 0$, we often
refer to \eqref{LP} as a \emph{diagonal} linear program. We denote the \emph{feasible set} of \eqref{LP} by
\begin{equation*}
\begin{aligned}
  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
\end{aligned}
\end{equation*}
A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$
is called a \emph{solution} to \eqref{LP} if $p^* = \left\langle c,x^*\right\rangle$.
